Ten Simple Rules for Teaching Programming

### 2017-08-10 paper.tex
Trialling the idea of adding an evidence strength measure.

@@

\rulemajor{There is no geek gene}{gene}

@@

\rulemajor{Use peer instruction}{peer-instruction}

@@

\rulemajor{Use live coding}{live-coding}

@@

\rulemajor{Have students make predictions}{predictions}

@@

\rulemajor{Use pair programming}{pair-programming}

@@

\rulemajor{Use worked examples with labelled subgoals}{worked-examples}

@@

\rulemajor{Stick to one language}{one-language}

@@

\rulemajor{Use authentic tasks}{authentic-tasks}

@@

To help students accomplish a visible and satisfting result
quickly, instructors can provide some pre-written software libraries or source code that start students
closer to the end goal.  The idea that students must start from scratch and write all the code they need
themselves is the relic of a bygone era of home microcomputers (and it was not true even then).
Pick the task that you actually want to the students to engage in, and provide everything else pre-made.

\rulemajor{Remember that novices are not experts}{not-experts}

@@

\rulemajor{Don't just code}{not-just-code}

@@

We are grateful to Barbara Ericson for her comments on a draft of this article.

>>>>

% To hide this, toggle the two macros below:
%\newcommand{\evidence}[1]{}
\newcommand{\evidence}[1]{\vspace{-0.3cm}\textbf{Evidence strength: #1}\vspace{0.5cm}}

@@

\rulemajor{There is no geek gene}{gene}
\evidence{Medium\footnote{Our evidence strength is an informal assessment, factoring in whether the effect has been replicated, and whether it has been shown specifically in computing, or only in other disciplines from which we believe it will transfer.}}

@@

\rulemajor{Use peer instruction}{peer-instruction}
\evidence{Very high}

@@

\rulemajor{Use live coding}{live-coding}
\evidence{Low}

@@

\rulemajor{Have students make predictions}{predictions}
\evidence{Low}

@@

\rulemajor{Use pair programming}{pair-programming}
\evidence{High}

@@

\rulemajor{Use worked examples with labelled subgoals}{worked-examples}
\evidence{High}

@@

\rulemajor{Stick to one language}{one-language}
\evidence{Low}

@@

\rulemajor{Use authentic tasks}{authentic-tasks}
\evidence{Medium}

@@

To help students accomplish a visible and satisfying result
quickly, instructors can provide some pre-written software libraries or source code that start students
closer to the end goal.  The idea that students must start from scratch and write all the code they need
themselves is the relic of a bygone era of home microcomputers (and it was not true even then).
Pick the task that you actually want to the students to engage in, and provide everything else pre-made.

\rulemajor{Remember that novices are not experts}{not-experts}
\evidence{Medium}

@@

\rulemajor{Don't just code}{not-just-code}
\evidence{Medium}

@@

We are grateful to Barbara Ericson and Leo Porter for their comments on a draft of this article.
